\documentclass[a4paper,9pt]{extarticle}

% Packages
\usepackage[utf8]{inputenc} % For input encoding
\usepackage{geometry} % For page margins
\geometry{a4paper, top=0.75in, bottom=0.5in, left=0.75in, right=0.75in} % Set paper size and margins
\usepackage{titlesec} % For section title formatting
\usepackage{enumitem} % For itemized list formatting
\usepackage{hyperref} % For hyperlinks
\usepackage{multicol} % For two-column layout
\usepackage{fancyhdr} % For page headers
\usepackage{xcolor} % For color customization
\usepackage{tabularx} % For date alignment
\usepackage{multirow} % For multi-row cells in tables
\usepackage{fontawesome} % For icons
\usepackage{setspace} % For line spacing

% Formatting
\setlist{noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt} % Removes item separation
\titleformat{\section}{\large\bfseries}{\thesection}{1em}{}[\titlerule] % Section title format
\titlespacing*{\section}{0pt}{0.5\baselineskip}{0.5\baselineskip} % Section title spacing
\setlength{\columnsep}{15pt} % Adjust column separation
\setlength{\parskip}{2pt} % Adjust paragraph spacing
\setstretch{1.1} % Adjust line spacing

% Hyperlink formatting
\hypersetup{colorlinks=true, linkcolor=black, urlcolor=blue}

% Begin document
\begin{document}

% Disable page numbers
\pagestyle{empty}

% Header
\begin{center}
\vspace*{-10pt} % Adjust this value to move the name higher or lower
\textbf{\LARGE EMMANUEL LE HIR}\\
\vspace{5pt} % Adjust this value to control the space below the name
\textbf{6-month end-of-studies international internship starting March 2025} \\
\vspace{3pt}
Email: \href{mailto:emmanuel@lehir.bzh}{emmanuel@lehir.bzh} -- Mobile: +33 (0)6 28 91 76 28 -- Address: 5 Rue d'Odessa, 75014 Paris, France
\end{center}

\section*{Professional Summary}
Motivated final year student in applied mathematics and economics, seeking an international end-of-studies internship in consulting starting March 2025. Strong background in strategic planning, business development, and transformation. Experienced in leveraging quantitative skills to solve complex management challenges.

\section*{Work Experience}

\begin{tabularx}{\textwidth}{@{}Xr@{}}
\textbf{Saint-Gobain -- Multinational Industrial Conglomerate} & Paris, France\\
\textit{Data Science Intern} & April 2024 — August 2024\\
\end{tabularx}
\vspace{-5pt}
\begin{itemize} \itemsep -1pt
    \item Projects automation to accelerate business development.
    \item Developed a Python library to streamline the use of AI for internal operations, while ensuring compliance with the group’s confidentiality policies, enhancing productivity and decision-making processes.
\end{itemize}

\vspace{5pt}
\noindent
\begin{tabularx}{\textwidth}{@{}Xr@{}}
\textbf{EY -- Global Business Services} & Paris, France\\
\textit{Financial Audit Intern} & September 2023 — March 2024\\
\end{tabularx}
\vspace{-5pt}
\begin{itemize} \itemsep -1pt
    \item Assisted in executing financial audits for major clients, ensuring data accuracy and regulatory compliance.
    \item Identified discrepancies and risks in financial data, working closely with senior auditors to enhance internal controls.
    \item Contributed to the preparation of detailed audit reports, delivering actionable insights that improved client financial strategies and operations.
\end{itemize}

\section*{Education}

\begin{tabularx}{\textwidth}{@{}Xr@{}}
\textbf{École des Mines -- Engineering School} & Nancy, France\\
\textbf{MSc} in Applied Mathematics and Decision Engineering & 2021 — Expected 2025\\
\end{tabularx}
Relevant coursework: \textit{Mathematical Modelling, AI \& Computer Science, Statistics \& Probabilities.}

\vspace{5pt} % Increase space between entries
\noindent
\begin{tabularx}{\textwidth}{@{}Xr@{}}
\textbf{Faculty of Law, Economics, and Management} & Nancy, France\\
\textbf{Master’s Degree} in Energy and Digital Transition Economics & 2022 — Expected 2025\\
\end{tabularx}
Relevant coursework: \textit{Econometrics, Risk Analysis, Energy Policy Evaluation, Financial Management}.

\vspace{5pt} % Increase space between entries
\noindent
\begin{tabularx}{\textwidth}{@{}Xr@{}}
\textbf{Lycée Charlemagne -- Engineering Preparation Classes} & Paris, France\\
Preparatory course for competitive exams & 2018 — 2021\\
\end{tabularx}
Relevant coursework: \textit{Mathematics, Physics.}

\vspace{5pt} % Increase space between entries
\noindent
\begin{tabularx}{\textwidth}{@{}Xr@{}}
\textbf{École Alsacienne -- High School} & Paris, France\\
French Baccalaureate, Scientific Section, with Highest Honors & 2018\\
\end{tabularx}

\section*{Skills}
\noindent
\begin{minipage}[t]{0.45\textwidth} % Ajuste la largeur selon tes besoins
    \textbf{Languages:}
    \begin{itemize}
        \item French (native)
        \item English (fluent C1 -- \textit{IELTS 7.5/9})
        \item Spanish (intermediate B2/C1 -- \textit{SIELE} 815/1000)
    \end{itemize}
\end{minipage}%
\hfill % Espacement flexible
\begin{minipage}[t]{0.45\textwidth} % Ajuste la largeur selon tes besoins
    \textbf{Programming:}
    \begin{itemize}
        \item \textit{Programing Languages:} Python, R, VBA, SQL, MongoDB, MatLab, LaTeX, HTML/CSS
        \item \textit{Libraries/Frameworks:} Pandas, NumPy, Scikit-learn, TensorFlow, Keras, Microsoft Office
        \item \textit{Version Control:} Git, GitHub, Microsoft Azure
    \end{itemize}
\end{minipage}

\section*{Activities \& Interests}
\begin{itemize}
\item \textbf{Music:} Advanced piano practice; graduate of the Conservatoire Darius Milhaud in Paris. Courseworks includes music theory, chamber music, sight-reading, transposition, and choir.
\item \textbf{Student Associations:}
\begin{itemize}
\item Chief Administrative Officer, \href{https://mines-services.fr/}{Mines Student Consultancy} -- Managed a team of 30, established partner relations
\item Events Manager, \href{https://www.bdeminesnancy.com/bds}{Student Sports Association} -- Organized regional sport events for over 1,000 participants and managed Mines Nancy's delegation in national ones.
\item Participant, \href{https://cce.fr/}{Course Croisière de l’EDHEC} -- Assisted in securing sponsors. Team sport competition.
\end{itemize}
\item \textbf{Sports:} Regular practice in tennis, climbing, and football. Accomplished long-distance hikes and biking trips, including GR20 and sections of GR5 European trails, as well as a biking trip along the Croatian coast. Actively interested in motorsports, including MotoGP, FIM EWC, WRC, WEC, and F1.
\end{itemize}

\end{document}